Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-16 IEEE_ConferenceOnGames/new_article.tex
all corrections and  questions of  JJ addressed

    These structures represent individuals in the evolutionary algorithm. Once
    an individual is created it is ready to be evaluated in a simulation on the
    game environment. %In Laura's work, we tried to avoid this because it took a long time. Is there any procedure to check constraints and not evaluate them? - JJ
    % I will comment that we could work on that. At the moment each one is evaluated. - M

    Using a similar approach as the composite generator, all
    individuals have a maximum of ten seconds to maintain balance or reach
    absolute stability. If that happens  it means one of two
    things, first the generated structure is completely stable or second, the
    tower fell to either side and the pieces were destroyed or stopped moving by
    gravitational pull, when either of this happens by more than two seconds the
    simulation ends regardless of time remaining and the next individual is
    simulated.

    The evaluation process for this project is still in the development stages,
    and in our experience is one one of the more difficult components in this
    kind of systems. In this stage of the evolution, we first need to assign a
    good fitness to those structures that keep their balance and not fall apart.
    There are other variables we take in to account, but they will be explained
    later. In this initial stage, each individual in the population has 100
    points so before the simulation starts each of them are viable candidates to
    be an Elite % Elite? - JJ
    % But I think the problem remains, there is no difference even if they all have
    % zero points. But randomess in the selection coyuld do that. - Mario
    member of the population regardless of their relative height or
    complexity.

    First, after each of the individual simulations are over the evaluation process
    takes place, in this phase the resulting level is checked for those blocks that
    survived, that is,  not destroyed by falling. Every one
    of them is counted and then the resulting number is compared to the
    initial quantity of pieces  before the simulation. Each block represents a certain percentage of 100\% so the missing pieces 
    are subtracted from the total. In this moment, each block is counted as if 
    it was not a member of a composite, this is because after the simulation there is
    only data about each individual block. % What is a composite? The fitness is only the number of remaining blocks? Even if they are in the floor?

@@

    Other aspects that the system need to improve is in the processing time
    required, since the current way to calculate the fitness and create the next
    generations of a population requires the system to execute
    simulations of the levels on every generation that passes, therefore increasing
    the time it takes to complete an entire cycle of execution. In order to
    change this we require to create a way to evaluate a level using only the
    information of the pieces, locations and pigs locations and using this data to
    predict the way a level will behave when placed in a real simulation environment
    therefore drastically reducing execution times. %You can also take into account restrictions without simulation, as we do in our paper, or use a Physics engine - JJ

    We were able to fulfill our objective of generating levels that could be played;
    however, as seen in our figures, the current state of this system is still in the development 
    phase, and some modifications must be applied in order to optimize some aspects of it. For instance  
    by using a different way of generating individual we were able to reduce the process 
    time required on a full system execution; however we need to search for a way to 
    avoid using the software to evaluate the individuals, this way we expect to reduce 
    drastically the time required to process the data of the levels.  % Cite our paper, where we do exactly that - JJ

>>>>

    These structures represent individuals in the evolutionary algorithm. Once
    we create an individual, it is ready to be evaluated in a simulation on the
    game environment.  It is important to note that this is the most
    time-consuming task of the process. We could benefit from using alternative
    techniques like the one proposed by Calle et al. \cite{lauracalle}, where
    only those individuals that meet certain restrictions are candidates for a
    run in the simulator.
    %In Laura's work, we tried to avoid this because it took a long time. Is there any procedure to check constraints and not evaluate them? - JJ
    % Added a comment about this  - M 
    Using a similar approach as the composite generator, all
    individuals have a maximum of ten seconds to maintain balance or reach
    absolute stability. If that happens  it means one of two
    things, first the generated structure is completely stable or second, the
    tower fell to either side and the pieces were destroyed or stopped moving by
    gravitational pull, when either of this happens by more than two seconds the
    simulation ends regardless of time remaining and the next individual is
    simulated.

    The evaluation process for this project is still in the development stages,
    and in our experience is one one of the more difficult components in this
    kind of systems. In this stage of the evolution, we first need to assign a
    good fitness to those structures that keep their balance and not fall apart.
    There are other variables we take in to account, but they will be explained
    later. 
    % I commented the paragraph below because IMHO the reasoning is not right - Mario 
    %In this initial stage, each individual in the population has 100
    %points so before the simulation starts each of them are viable candidates to
    %be an Elite % Elite? - JJ

    % But I think the problem remains, there is no difference even if they all have
    % zero points. But randomess in the selection coyuld do that. - Mario

    %member of the population regardless of their relative height or
    %complexity.

    First, after all of the individual simulations are over the evaluation
    process takes place, in this phase the resulting levels are checked for those
    blocks that survived, that is,  they were not destroyed by falling. Every one of them
    is counted and then the resulting number is compared to the initial quantity
    of pieces found before the simulation started. Each block represents a certain percentage
    of 100\% so the missing pieces are subtracted from the total. In this
    moment, each block is counted as if it was not a member of a composite, this
    is because after the simulation there is only data about each individual block. 
    % What is a composite? There is a whole section devoted to explaining just that :) - Mario 
    % The fitness is only the number of remaining blocks? Even if they are in the floor? 
    % Yes, they some time form nice structures. We used to take height into account, but is not 
    % that important.  - Mario 
    % Will comment on it, after checking with Jaime if I'm right.

@@

    Other aspects that the system need to improve is in the processing time
    required, since the current way to calculate the fitness and create the next
    generations of a population requires the execution of many 
    simulations on every generation, therefore increasing
    the time it takes to complete an entire cycle of execution. In order to
    change this we require to create a way to evaluate a level using only the
    information of the pieces, locations and pigs locations and using this data to
    predict the way a level will behave when placed in a real simulation environment
    therefore drastically reducing execution times. We could take into account restrictions 
    needed to run a simulation, as it is done by Calle et al. \cite{lauracalle}, 
    or use a Physics engine that is optimiezed for this task.

    We were able to fulfill our objective of generating levels that could be played;
    however, as seen in our figures, the current state of this system is still in the development 
    phase, and some modifications must be applied in order to optimize some aspects of it. For instance  
    by using a different way of generating individual we were able to reduce the process 
    time required on a full system execution; however we still need to work on this problem as
    we mention before.  % Cite our paper, where we do exactly that - JJ 
                        % Done - Mario
